---
title: "10-import"
output: html_notebook
---

# Install Library 

```{r library}
library(readr)
library(tidyverse)
library(dplyr)
library(assertr)
library(janitor)
library(stringr)
library(glue)
```

# 1. Describe the data and the problem 

This dataset describes the listing activity and metrics in NYC, NY for 2019. I will try to predict the airbnb price in NYC region. The following list presents 16 variables in this datasets

id:Each Airbnb apartment has its own ID
name:Description of the features of certain Airbnb apartment 
host_id:Every host has his or her own ID
host_name:The name of the host 
neighbourhood_group:Five big region in NYC:Bronx, Brooklyn, Manhattan, Queens and Staten Island
neighbourhood:More specific neighbourhood names of the Airbnb apartment
latitude:Latitude data for Airbnb addresses
longitude:Longitude data for Airbnb apartment addresses
room_type:"Entire home/apt" & "Private room" & "Shared room"  
price:the price of certain Airbnb apartment
minimum_nights:Minimum numbers of nights to book  
number_of_reviews:Number of reviews this Airbnb apartment received from its customers 
last_review:Last review's data 
reviews_per_month:Number of reviews per month
calculated_host_listings_count:Total numbers of Airbnb apartment this host have in NYC.  
availability_365:How many days a year can this Airbnb apartment be available for customers to book

# 2. Read in and check data

(1)I import my data here
(2)I use the function head(), str(), dim() and summary() to read the data and have a general idea about the datasets.
(3.1)Then I check the data by using verify () There is no violation in colomn "id"; "host_id"; "neighbourhood_group"; "neighbourhood"; "latitude"; "longitude"; "room_type"; "price"; “minimum_nights”; “number_of_reviews”;“calculated_host_listings_count”; “availability_365” which means all the numbers are not na.There 16 na numbers in “name" column; 21 na numbers in "host_name" column; 10052 na numbers in "last_review" column and "reviews_per_month" column. 
(3.2)I check the bounds of some columns and I find there are 14 unusual data in "minium_night" column. They've been renting on airbnb for more than a year.

Import Data 
I import my data here
```{r import data}
AB_NYC_2019 <- read_csv("AB_NYC_2019.csv")
View(AB_NYC_2019)
```

Read Data 
I use the function head(), str(), dim() and summary() to read the data and have a general idea about the datasets.
```{r read data}
head(AB_NYC_2019)
str(AB_NYC_2019)
dim(AB_NYC_2019)
summary(AB_NYC_2019)
```

Check NA 
I check the data by using verify () There is no violation in colomn "id"; "host_id"; "neighbourhood_group"; "neighbourhood"; "latitude"; "longitude"; "room_type"; "price"; “minimum_nights”; “number_of_reviews”;“calculated_host_listings_count”; “availability_365” which means all the numbers are not na.There 16 na numbers in “name" column; 21 na numbers in "host_name" column; 10052 na numbers in "last_review" column and "reviews_per_month" column. 
```{r check data na 1}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[1]))
```

```{r check data na 2}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[2]))
```

```{r check data na 3}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[3]))
```

```{r check data na 4}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[4]))
```

```{r check data na 5}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[5]))
```

```{r check data na 6}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[6]))
```

```{r check data na 7}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[7]))
```

```{r check data na 8}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[8]))
```

```{r check data na 9}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[9]))
```

```{r check data na 10}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[10]))
```

```{r check data na 11}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[11]))
```

```{r check data na 12}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[12]))
```

```{r check data na 13}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[13]))
```

```{r check data na 14}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[14]))
```

```{r check data na 15}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[15]))
```

```{r check data na 16}
AB_NYC_2019 %>%
  verify(!is.na(AB_NYC_2019[16]))
```

Check bounds 
I check the bounds of some columns and I find there are 14 unusual data in "minium_night" column. They've been renting on airbnb for more than a year.
```{r cheack bounds price}
AB_NYC_2019%>%
  assert(within_bounds(0,90000),price)
```
  
```{r cheack bounds minimum nights}
AB_NYC_2019%>%
  assert(within_bounds(0,365),minimum_nights)
```

# 3. Clean up the data

(1)I use clean_names() function to clean the name of columns. 
(2)I convert the numeric na data to 0. Since the numeric data is last review column, people didn't review thus the "last review" column's na is 0. 
(3)I convert the "neighbourhood_group" column to factors. 
(4)I transfer the content to lower case in "name" column. 

Clean names 
I use clean_names() function to clean the name of columns.
```{r clean data: clean names}
AB_NYC_2019%>%
  clean_names()
```

Make NA to 0
I use clean_names() function to clean the name of columns. 
```{r clean data: make na to 0}
AB_NYC_2019<-AB_NYC_2019 %>%
  mutate_if(is.numeric, ~replace(., is.na(.), 0))
```

Covert factors 
I will label the column neigbourhood_group into five differnt groups later so I convert this column into factors.
```{r clean data: convert factors}
AB_NYC_2019<-AB_NYC_2019%>%
  mutate(neighbourhood_group=factor(neighbourhood_group))
```

Low case column "name"
Column "name" is descriptions of the feature of certain Airbnb apartment. Therefore, I want to unify the
content of column "name" to lower case. 
```{r clean data: lower case column name }
AB_NYC_2019<-AB_NYC_2019%>%
  mutate(name=str_to_lower(name))
```