---
title: "40-modeling"
output: html_notebook
---

# 5. Prepare data for modelling 

I create a new dataframe named "data_prepare" which including the new freatue colunms that I create above and I also borrow some important columns from orignal AB_NYC_2019 dataframe. Then I write it as a new csv and output it for later analysis. 
```{r data prepare}
data_prepare<-AB_NYC_2019%>%
  labeled_distinct_regions(neighbourhood_group)%>%
  name_with_luxury(name)%>%
  #last_review_by_year(last_review)%>%
  #availability_per_day(availability_365)%>% 
  select(labeled_distinct_regions,name_with_luxury,room_type,minimum_nights,number_of_reviews,reviews_per_month) #,last_review_by_year,availability_per_day)

#delete the # sign above and run the features that you compelte in 30-feature-engineering

data_prepare

write.csv(data_prepare,"data_prepare.csv")
```

# 6. Test features 

## 4.1 Feature engineering:Locaton of an Airbnb apartment 
weather distinct regions in NYC have been labeled as 1,2,3,4,5 
```{r test function 4.1}
data_prepare%>%
  assert(in_set(1,2,3,4,5),labeled_distinct_regions)
```

## 4.2 Feature engineering:filer the descriptions of Airbnb aprtment with the word "luxury" 
weather "name" (description) column show up the word "luxury". One description contains luxury two times but most are one time and some descriptions do not have word "luxury" in it. 
```{r test function 4.2}
data_prepare%>%
  assert(in_set(0,1,2),name_with_luxury)
```

## 4.3 Feature engineering:last view by year 
use the verify() or assert() function the test the bound.It is 2019 NYC dataset, the last view by year can't be 2020 or 1900.  
```{r test function 4.3}

```

## 4.4 Feature engineering: availablity per day
use the verify() or assert() function the test the bound. Since it is the ratio of availablity per day so it should be in the range of [0,1]
```{r test function 4.4}

```
